---
Data Science Training
Problem 01
---
01) Create two variables, Ana and Paulo, and assign them the values of their ages, 8 and 12 years respectively. The variables must be of integer type. Print to the console "The girl is older" or "The boy is older" as the result of a logical test.
```{r}
# Creating the variables and assign them the values of their ages
Ana <- 8L
Paulo <- 12L
# Verifing if the variables are integer type
class(Ana)
class(Paulo)
# Creating the logical test that will verify if the girl or the boy is older
logicaltest = ifelse(Ana > Paulo, "The girl is older", "The boy is older")
# Printing into the console who is older
logicaltest
```

02) BOD is an existing object in R. Check the class of this object.
```{r}
class(BOD)
```

03) Create a vector that stores numbers from 1 to 10 and then print the even values.
```{r}
X <- c(1,2,3,4,5,6,7,8,9,10)
X
class(X)
```

04) women is an existing dataframe in R. Print the last 10 lines.
```{r}
tail(women)
```

05) Use the R plot function to produce a graph of the Sepal.Width and Petal.Length attributes of the Iris dataset. The graph should only print lines 50 through 100.
```{r}
plot(
  iris$Sepal.Width[50:100],
  iris$Sepal.Length[50:100],
  xlab = "Sepal Width",
  ylab = "Petal Length",
  main = "Iris dataset"
)
```

06) Create two vectors of equal size, add the equivalent positions of the vectors, and print the result.
```{r}
# Creating the vectors of equal size
v1 <- c(1,2,3)
v2 <- c(4,5,6)
# Adding the equivalent positions
result <- v1 + v2
# Printing the result
result
```

07) Print the number of rows, columns, row names, and column names for the CO2 dataset.
```{r}
# Number of rows
nrow(CO2)

# Number of columns
ncol(CO2)

# Row names
row.names(CO2)

# Column names
colnames(CO2)
```

